GlasSees - Providing Context Menus for the Real World Through Head-Worn Infrared Targeting

### 2013-09-18 doc/sigchi14/introduction.tex
take out 'see'

In this paper, we introduce a novel method for selecting and controlling smart appliances in physical spaces through the use of a head-worn computing device with near-eye display and wireless communication. We augment Google Glass\footnote{\url{http://www.google.com/glass/start/}} with custom hardware for this purpose. Users first look in the direction of the device they wish to control to initiate interaction (e.g., at a lamp to control lighting, or at a speaker to change music playback volume).  If multiple devices fall within communication range, a disambiguation technique that combines on-screen information as well as visual feedback on the target devices lets users select their desired target. Once acquired, a device specific control UI shown on the head-mounted display enables adjustment of discrete and continuous parameters through a touchpad interface (see Figure~\ref{fig:teaser}).

>>>>

In this paper, we introduce a novel method for selecting and controlling smart appliances in physical spaces through the use of a head-worn computing device with near-eye display and wireless communication. We augment Google Glass\footnote{\url{http://www.google.com/glass/start/}} with custom hardware for this purpose. Users first look in the direction of the device they wish to control to initiate interaction (e.g., at a lamp to control lighting, or at a speaker to change music playback volume).  If multiple devices fall within communication range, a disambiguation technique that combines on-screen information as well as visual feedback on the target devices lets users select their desired target. Once acquired, a device specific control UI shown on the head-mounted display enables adjustment of discrete and continuous parameters through a touchpad interface (Figure~\ref{fig:teaser}).
